\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-06-09 OneStepConvergence.tex
Update on Overleaf.

\begin{document}

These notes are an attempt of writing the one-step convergence of the particle system to a PDE limit.

@@

In this document we assume we have the particle system with (unscaled) birth rate constant and equal $1$ and death rate at position $x$ given by $1+F(\rho_\epsilon*\overline{\eta}(x))/\theta$. That is, the martingale problem for the scaled system $\overline{\eta}_t$, is that for any smooth function $\phi$ we can write
\begin{align}
&\langle\phi(x),\overline{\eta}_{t}(dx)\rangle-\langle\phi(x),\overline{\eta}_{0}(dx)\rangle = M_t(\phi)   + \int_{0}^{t}\langle \theta  \int_{\mathbb{R}^d} \left( \phi(y)-\phi(x)\right) q_\theta(x,dy), \overline{\eta}_s^\epsilon(dx) \rangle ds \nonumber \\
 & + \int_0^t \langle  F(\langle \rho_\epsilon(y-x), \overline{\eta}_s(dy) \rangle)\phi(x),\overline{\eta}_s^{\varepsilon, \theta, N}(dx)  \rangle ds. \label{mgp1}
\end{align}
where $M_t(\phi)$ is a martingale with quadratic variation:
\begin{align}
[M(\phi)]_t&:=\frac{\theta}{N}\int_{0}^{t}\bigg\{ \left\langle \int_{\mathbb{R}^d} \phi^2(y) q_\theta(x,dy), \overline{\eta}_s^{\varepsilon, \theta, N}(dx) \right\rangle \nonumber\\
&+ \left\langle  \left(2 + \frac{F(\langle \rho_\epsilon(y-x), \overline{\eta}_s(dy)\rangle )}{\theta } \right)\phi^2(x), \overline{\eta}_s^{\varepsilon, \theta, N}(dx))\right\rangle   \bigg\}ds.  \label{mgp2}
\end{align}

@@

We will assume $\overline{\eta}_0:=\overline{\eta}_0(\epsilon,N,\theta)$ is a sequence of initial conditions for $(\overline{\eta}_t)_{t \geq 0}$ such that there exists a finite constant $C>0$ independent of $\epsilon, N, \theta$, 
\begin{enumerate}
\item $\langle 1 , \overline{\eta}_0 \rangle < C $
\item  $\Vert \rho_\epsilon * \overline{\eta}_0(x) \Vert_\infty < C$ for all $x \in \mathbb{R}^d$
\item $|\rho_\epsilon * \overline{\eta}_0(x) - \rho_\epsilon * \overline{\eta}_0(y)| \leq C \Vert x - y \Vert  $ for all $x,y \in \mathbb{R}^d$
\item $(\rho_\epsilon * \overline{\eta}_0(x) dx) \Rightarrow u_0(x)dx$ for some $u_0(x) \in \mathcal{C}^2(\mathbb{R}^d)$, where $\Rightarrow$ denotes weak convergence. 
\end{enumerate}
Furthermore, suppose that,
\begin{equation}
\frac{\theta}{\epsilon^d N} + \frac{1}{\theta \epsilon^{2}}\rightarrow 0 \label{ConditionsForConvergence}
\end{equation}
Fix $T>0$. Then, the measure $((\rho_\epsilon *\overline{\eta}_t)(x) dx)_{t \geq 0}$ converges weakly in $D([0,T], \mathcal{M}_F(\mathbb{R}^d))$ to a measure $(\Xi_t(dx))_{t \geq 0}$. Moreover, up to a modification on a set of measure zero, $\Xi_t(x) = u_t(x)dx$, where $u_t(x)$ is a weak solution to:
\[ \partial_t u = \frac{1}{2}\Delta u + u F(u) \]
with initial condition $u_0$. That is, for every smooth function with compact support $f$ and $t>0$, we have:
\begin{equation*}
 \int \partial_t  u_t(x) f(x) dx = \int u_t(x)\frac{1}{2} \Delta f(x) dx + \int f(x) u_t(x) F(u_t(x)) dx.
\end{equation*}
\end{theorem}
 \todo[inline]{Question: Why do we need that regularity on $u_0$? I believe all we need is that (\ref{aprox3}) holds, and for that I am almost sure that $u_0$ only need to satisfy the first three hypothesis for $\overline{\eta}_0(x)$. Furthermore,  if I am not mistaken, those are all implied by $u_0(x) \in L^1(\mathbb{R}^d) \cap L^2(\mathbb{R}^d) \cap \mathcal{C}^1(\mathbb{R}^d)$ in case we want a nice space to put on the result.}

@@

\section{Preliminaries}
\subsection{Boundedness of the total mass}
\begin{lemma} \label{Lemma:UniformlyBoundedMass}
Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}, there is a finite constant $C$ (independent of $\epsilon, N, \theta$), such that $\EE\left[ \sup_{0 \leq s \leq T} \langle 1, \overline{\eta}_s \rangle \right] \leq C$.
\end{lemma}
\begin{proof}
By putting $\phi(x)=1$ in the martingale problem of $\overline{\eta}_t$, equation (\ref{mgp1}), we have,
\begin{align} \label{eq:MPTotalMass}
\langle 1, \overline{\eta}_t \rangle &= \langle 1, \overline{\eta}_0 \rangle + \int_0^t \langle F(\rho_\epsilon * \overline{\eta}_s), \overline{\eta}_s \rangle ds + M_t
\end{align}
where $M_t$ is a martingale with quadratic variation,
\begin{align} \label{eq:QVTotalMass}
[M]_t = \frac{\theta}{N}\int_0^t \langle 2 + \frac{F(\rho_\epsilon* \overline{\eta}_s)}{\theta}, \overline{\eta}_s \rangle d s 
\end{align}
By taking expectations in (\ref{eq:MPTotalMass}) we get,
\[ \EE[\langle 1, \overline{\eta}_t \rangle] =  \EE[\langle 1, \overline{\eta}_0 \rangle]  + \int_0^t \langle F(\rho * \overline{\eta}_s), \overline{\eta}_s \rangle ds ]   \leq C +   C \mathbb{E}\left[ \int_0^t \langle 1, \overline{\eta}_s \rangle ds \right].\] 
In last inequality we used that $F(x)1_{x >0}$ and $\langle 1, \overline{\eta}_0 \rangle$ are uniformly bounded above. By Gronwall's inequality we deduce $\EE[\langle 1, \overline{\eta}_s \rangle]$ is bounded on $[0,T]$. Hence, by taking expectations in (\ref{eq:QVTotalMass}) and using again the bound on $F(x)1_{x>0}$ we get,
\[ \EE\left[ [M]_t \right] \leq \frac{\theta}{N} C \int_0^t \mathbb{E}\left[ \langle 1, \overline{\eta}_s \rangle ds \right] \leq \frac{\theta}{N}C t \]
Note that, with this, $\EE[ [M]_t]$ is bounded (and in fact $\mathcal{O}(\theta/N)$). By the Burkholder-Davis-Gundy inequality and then's Jensen inequality we get
\begin{align*} \EE\left[ \sup_{0 \leq t \leq T} M_t \right] \leq C \EE\left[ [M]_T^{1/2} \right] \leq C \EE[M]_T^{1/2} \leq C   \end{align*}
Taking supremum and then expectation in (\ref{eq:MPTotalMass}) and using the last inequality gives the result.
\end{proof}

@@

\begin{lemma} \label{PsiBoundHS}
Fix $t>0$ and let $T(t)$ be a random variable such that $\theta T(t) \sim Poisson(\theta t)$. Then:
\[ \psi^{\epsilon,x}_t(y) = \mathbb{E}\left[ p_{\epsilon^2+T(t)}(x,y)\right] \]
Moreover,
\[ \Vert \psi^{\epsilon,x}_t \Vert_\infty \leq \mathcal{O}\left( \frac{1}{(t+\epsilon^2)^{d/2}} + \frac{1}{\epsilon^2 \theta} \right) \]
\end{lemma}
\begin{proof}
The first claim of this result follows immediately from $\mathcal{L}^\theta$ being the generator of a continuous random walk, where jumps with mean $0$ and variance $1/\theta$ arrive at rate $\theta$.

@@

For every $x \in \mathbb{R}^d$ and $t>0$ we have,

@@

|\psi_t^{\epsilon,x} - p_{\epsilon^2+t}(x,y)| &\leq \frac{C}{\epsilon^2 \theta}\left(\psi_t^{\epsilon,x}(y) + p_{\epsilon^2+t}(x,y) + p_{3/2(\epsilon^2+t)}(x,y)+p_{3(\epsilon^2+t)}(x,y) \right)

@@

\subsection{The martingale problem for a time dependent function.}
Before proceeding we do the following observation. For any time, dependent function $\phi_t(x)$ the martingale problem for $\overline{\eta}_t$, (\ref{mgp1}), gives that
\begin{align}
\langle \overline{\eta}_t(dx), \phi_0(x)\rangle &= \langle \overline{\eta}_0(dx), \phi_t(x)\rangle +  M_t(\phi_\cdot(\cdot)) - \int_0^t \langle \partial_t \phi_{t-s}(x), \overline{\eta}_s(dx) \rangle  ds \nonumber \\ & + \int_0^t \langle \mathcal{L}^\theta \phi_{t-s}(x), \overline{\eta}_s(dx) \rangle ds+ \int_{0}^t \langle \phi_{t-s}(x)F (\rho_\epsilon*\overline{\eta}_s)(x) ) , \overline{\eta}_s(dx) \rangle ds \label{timeMGP}
\end{align}
with $M_t(\phi_\cdot(\cdot))$ a martingale with having quadratic variation:
\[ [M(\phi_\cdot(\cdot))]_t = \frac{\theta}{N}\int_0^t \langle \int_{\mathbb{R}^d} \phi_s(z)^2 q_\theta(y,dz) + \left( 2 + \frac{F(\rho_\epsilon*\overline{\eta}_s(y))}{\theta}\right) \phi_s(y)^2, \overline{\eta}_s(dy) \rangle ds \]
\section{Tightness}

\subsection{Uniform bound for $\{ \rho_\epsilon * \overline{\eta}_s (x)\}_{0 \leq s \leq T}$ for fixed $T$}
\begin{lemma} \label{FirstBoundLocalDensity}
Under the conditions of Theorem~\ref{TeoremOneStepConvergence} there is a constant $C>0$ (independent of $\epsilon, N, \theta, x$ and $T$) such that,
\[ \EE[ \rho_\epsilon*\overline{\eta}_t(x) ] < C \]
for all $t \in [0,T]$ and $x \in \mathbb{R}^d$.
\end{lemma}
\begin{proof}
Recall $\psi_t^{\epsilon,x}$, the solution of (\ref{AlmostHeatEquation}) with initial condition $\psi_0^{\epsilon,x}(y)=\rho_\epsilon(y-x)$. By replacing $\phi_t$ with $\psi_t^{\epsilon,x}$ in (\ref{timeMGP}) we can write,
\begin{align}
(\rho_\epsilon*\overline{\eta}_t(x)) = \langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle  + \int_0^t \langle \psi_{t-s}^{\epsilon,x}(y) F(\rho_\epsilon*\overline{\eta}_s(y)), \overline{\eta}_s(dy) \rangle ds + M_t \label{MartingaleProblemMolifier}
\end{align}
where $F$ is uniformly bounded above. Hence, if we take expectation,
\begin{align}
\EE[\rho_\epsilon * \overline{\eta}_t(x)]&= \EE[\langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle] + C \EE[\int_0^t \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy) \rangle ds] \nonumber \\ & \leq  \EE[\langle p_{\epsilon^2+T(t)}(x,y),\overline{\eta}_0(dy)\rangle] + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty \EE[\sup_{0 \leq s \leq t} \langle 1, \overline{\eta}_s(dy) \rangle] ds \\ & \leq C + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty ds \label{BoundForMolifier}
\end{align}
Where in the last inequality we used Lemma~\ref{Lemma:UniformlyBoundedMass} and our first assumption on the initial condition. Furthermore, using Lemma \ref{PsiBoundHS} we can bound $\Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty$ by $C (t-s+\epsilon^2)^{-d/2}$. In dimension one the reminding term is immediately uniformly bounded. For $d=2$ we can iterate. By using again the martingale problem and the same arguments we used to get (\ref{BoundForMolifier}) we get,
\begin{equation} \label{IterationBoundPsi}
\EE[\langle \psi_{t-s}^{\epsilon,x}, \overline{\eta}_s(dy)\rangle] \leq \EE[\langle \psi_{t}^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle]  + C \int_0^s \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
\end{equation}
Hence, using (\ref{IterationBoundPsi}) in (\ref{BoundForMolifier}) gives
\begin{align*}
\EE[ \rho_\epsilon * \overline{\eta}_t(x)  ] &\leq \EE[\langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle] + \int_0^t C\langle \psi_{t}^{\epsilon,x}, \overline{\eta}_0(dy)\rangle ds + C^2 \int_0^t \int_0^s  \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du ds \\ &= (1+Ct) \EE[ \langle \psi_t^{\epsilon,x}, \overline{\eta}_0(dy) \rangle] + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du \\ &\leq C(1+t) + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
\end{align*}
which again is uniformly bounded using Lemma \ref{PsiBoundHS}. It is easy to see this iteration can be used to prove an uniform bound in any dimension.

@@

\begin{corollary}
Let $(M_t)_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}). Then
\[ \EE\left[ [M]_t \right] \leq \frac{C \theta}{ N \epsilon^{d}} \]
where $C$ is independent of $\epsilon,\theta,N$. \label{Cor:ControlQVMQ}
\end{corollary}
\begin{proof}
Indeed, note we can explicitly write the quadratic variation of $M_t$ by,
\[ [M]_t = \frac{\theta}{N} \int_0^t \langle \int_{\mathbb{R}^d} \psi_{t-s}^{\epsilon,x}(z)^2 q_\theta(y,dz) + \left(2+\frac{F(\rho_\epsilon * \overline{\eta}_s(y))}{\theta}\right)\psi_{t-s}^{\epsilon,x}(y)^2, \overline{\eta}_s(dy) \rangle  ds\]
using Lemma~\ref{PsiBoundHS} we can get the following bound,
\[ \psi_{t-s}^{\epsilon,x}(y)^2 \leq \psi_{t-s}^{\epsilon,x}(y) \frac{C}{(\epsilon^2+t-s)^{d/2}} \leq \frac{C}{\epsilon^d} \psi_{t-s}^{\epsilon,x}(y). \]
Hence, by using the last inequality the upper bound on $F(x)1_{x}$ we deduce that:
\begin{align*}
[M]_t &\leq \frac{C \theta}{\epsilon^d N} \int_0^t \left\{  \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy)\rangle \right\} ds 
\end{align*}
Taking expectations and using the bound of Lemma~\ref{FirstBoundLocalDensity} we get the result.
\end{proof}

>>>>

\begin{document}
These notes are an attempt of writing the one-step convergence of the particle system to a PDE limit.

@@

In this document we assume we have the particle system with (unscaled) birth rate constant and equal $1$ and death rate at position $x$ given by $1+F(\rho_\epsilon*\overline{\eta}(x))/\theta$. That is, the martingale problem for the scaled system $\overline{\eta}_t$, is that for any smooth function $\phi$ we can write
\begin{align}
&\langle\phi(x),\overline{\eta}_{t}(dx)\rangle-\langle\phi(x),\overline{\eta}_{0}(dx)\rangle = M_t(\phi)   + \int_{0}^{t}\langle \theta  \int_{\mathbb{R}^d} \left( \phi(y)-\phi(x)\right) q_\theta(x,dy), \overline{\eta}_s^\epsilon(dx) \rangle ds \nonumber \\
 & + \int_0^t \langle  F(\langle \rho_\epsilon(y-x), \overline{\eta}_s(dy) \rangle)\phi(x),\overline{\eta}_s^{\varepsilon, \theta, N}(dx)  \rangle ds. \label{mgp1}
\end{align}
where $M_t(\phi)$ is a martingale with quadratic variation:
\begin{align}
[M(\phi)]_t&:=\frac{\theta}{N}\int_{0}^{t}\bigg\{ \left\langle \int_{\mathbb{R}^d} \phi^2(y) q_\theta(x,dy), \overline{\eta}_s^{\varepsilon, \theta, N}(dx) \right\rangle \nonumber\\
&+ \left\langle  \left(1 + \frac{F(\langle \rho_\epsilon(y-x), \overline{\eta}_s(dy)\rangle )}{\theta } \right)\phi^2(x), \overline{\eta}_s^{\varepsilon, \theta, N}(dx))\right\rangle   \bigg\}ds.  \label{mgp2}
\end{align}

@@

We will assume $\overline{\eta}_0:=\overline{\eta}_0(\epsilon,N,\theta)$ is a sequence of initial conditions for $(\overline{\eta}_t)_{t \geq 0}$ such that there exists a finite constant $C>0$ independent of $\epsilon, N, \theta$, 
\begin{enumerate}
\item $\langle 1 , \overline{\eta}_0 \rangle < C $
\item  $\Vert \rho_\epsilon * \overline{\eta}_0(x) \Vert_\infty < C$ for all $x \in \mathbb{R}^d$
\item $|\rho_\epsilon * \overline{\eta}_0(x) - \rho_\epsilon * \overline{\eta}_0(y)| \leq C \Vert x - y \Vert  $ for all $x,y \in \mathbb{R}^d$
\item $(\rho_\epsilon * \overline{\eta}_0(x) dx) \Rightarrow u_0(x)dx$ for some $u_0(x) \in \mathcal{C}^2(\mathbb{R}^d)$, where $\Rightarrow$ denotes weak convergence. 
\end{enumerate}
Furthermore, suppose that,
\begin{equation}
\frac{\theta}{\epsilon^d N} + \frac{1}{\theta \epsilon^{2}}\rightarrow 0 \label{ConditionsForConvergence}
\end{equation}
Fix $T>0$. Then, the measure $((\rho_\epsilon *\overline{\eta}_t)(x) dx)_{t \geq 0}$ converges weakly in $D([0,T], \mathcal{M}_F(\mathbb{R}^d))$ to a measure $(\Xi_t(dx))_{t \geq 0}$. Moreover, up to a modification on a set of measure zero, $\Xi_t(x) = u_t(x)dx$, where $u_t(x)$ is a weak solution to:
\[ \partial_t u = \frac{1}{2}\Delta u + u F(u) \]
with initial condition $u_0$. That is, for every smooth function with compact support $f$ and $t>0$, we have:
\begin{equation*}
 \int \partial_t  u_t(x) f(x) dx = \int u_t(x)\frac{1}{2} \Delta f(x) dx + \int f(x) u_t(x) F(u_t(x)) dx.
\end{equation*}
\end{theorem}
 \todo[inline]{Question: Why do we need that regularity on $u_0$? I believe all we need is that (\ref{aprox3}) holds, and for that, I am almost sure that $u_0$ only needs to satisfy the first three hypotheses for $\overline{\eta}_0(x)$. Furthermore,  if I am not mistaken, those are all implied by $u_0(x) \in L^1(\mathbb{R}^d) \cap L^2(\mathbb{R}^d) \cap \mathcal{C}^1(\mathbb{R}^d)$ in case we want a nice space to put on the result.}
\todo[inline]{Questions 2: The conditions on $F$ implies that $F(x)1_{x>0} = (A-Bx)1_{x>0}$ for some $A,B>0$, or not? At least that is the only polynomial that is bounded above with a bounded derivative. Maybe we could rewrite the result for that explicit $F$?}

@@

\section{Preliminaries}
\subsection{Boundedness of the total mass}
\begin{lemma} \label{Lemma:UniformlyBoundedMass}
Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}, there is a finite constant $C$ (independent of $\epsilon, N, \theta$), such that $\EE\left[ \sup_{0 \leq s \leq T} \langle 1, \overline{\eta}_s \rangle \right] \leq C$.
\end{lemma}
\begin{proof}
By putting $\phi(x)=1$ in the martingale problem of $\overline{\eta}_t$, equation (\ref{mgp1}), we have,
\begin{align} \label{eq:MPTotalMass}
\langle 1, \overline{\eta}_t \rangle &= \langle 1, \overline{\eta}_0 \rangle + \int_0^t \langle F(\rho_\epsilon * \overline{\eta}_s), \overline{\eta}_s \rangle ds + M_t
\end{align}
where $M_t$ is a martingale with quadratic variation,
\begin{align} \label{eq:QVTotalMass}
[M]_t = \frac{\theta}{N}\int_0^t \langle 1 + \frac{F(\rho_\epsilon* \overline{\eta}_s)}{\theta}, \overline{\eta}_s \rangle d s 
\end{align}
By taking expectations in (\ref{eq:MPTotalMass}) we get,
\[ \EE[\langle 1, \overline{\eta}_t \rangle] =  \EE[\langle 1, \overline{\eta}_0 \rangle]  + \EE[ \int_0^t \langle F(\rho * \overline{\eta}_s), \overline{\eta}_s \rangle ds ]   \leq C +   C \mathbb{E}\left[ \int_0^t \langle 1, \overline{\eta}_s \rangle ds \right].\] 
In last inequality we used that $F(x)1_{x >0}$ and $\langle 1, \overline{\eta}_0 \rangle$ are uniformly bounded above. By Gronwall's inequality we deduce $\EE[\langle 1, \overline{\eta}_s \rangle]$ is bounded on $[0,T]$. Hence, by taking expectations in (\ref{eq:QVTotalMass}) and using again the bound on $F(x)1_{x>0}$ we get,
\begin{equation} \EE\left[ [M]_t \right] \leq \frac{\theta}{N} C \int_0^t \mathbb{E}\left[ \langle 1, \overline{\eta}_s \rangle ds \right] \leq \frac{\theta}{N}C t \label{eq:quadvarMass} \end{equation}
Note that, with this, $\EE[ [M]_t]$ is bounded (and in fact $\mathcal{O}(\theta/N)$). By the Burkholder-Davis-Gundy inequality and then's Jensen inequality we get
\begin{align*} \EE\left[ \sup_{0 \leq t \leq T} M_t \right] \leq C \EE\left[ [M]_T^{1/2} \right] \leq C \EE[M]_T^{1/2} \leq C   \end{align*}
Taking supremum and then expectation in (\ref{eq:MPTotalMass}) and using the last inequality gives the result.
\end{proof}
We will require also a second moment bound on the total mass.

\begin{proposition}
Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that, for all $t \in [0,T]$ and for big enough $N$ and $\theta$, $\EE[ \langle 1, \overline{\eta}_t \rangle^2] \leq C$.\label{Prop:SecondMomentMass}
\end{proposition} 
\begin{proof}
By using in (\ref{eq:MPTotalMass}) that, by assumption, $\langle 1, \overline{\eta}_0 \rangle$  and $F(x)1_{x > 0}$ are bounded above we get,
\begin{align*}
 \langle 1, \overline{\eta}_t \rangle^2 \leq C \langle 1, \overline{\eta}_t \rangle + C\langle 1,\overline{\eta}_t \rangle \int_0^t \langle 1, \overline{\eta}_s\rangle ds + M_t \langle 1, \overline{\eta}_t \rangle \end{align*}
Taking expectation we obtain,
\begin{align*}
\EE[ \langle 1, \overline{\eta}_t \rangle^2 ] & \leq C \EE[\langle 1, \overline{\eta}_t \rangle] + C\EE[  \langle 1,\overline{\eta}_t \rangle \int_0^t \langle 1, \overline{\eta}_s\rangle ds ] + \EE[ M_t \langle 1, \overline{\eta}_t \rangle] \\ & \leq C + C\EE[\frac{1}{2} \langle 1, \overline{\eta}_t\rangle^2] + \frac{1}{2} \EE[t \int_0^t \langle 1, \overline{\eta}_s \rangle^2 ds ] + (\EE[M_t^2] \EE[\langle 1, \overline{\eta}_t \rangle^2])^{1/2}
\end{align*}
where in the second inequality we have used Lemma~\ref{Lemma:UniformlyBoundedMass} on the first term, that $2ab \leq a^2 + b^2$ and Jensen's inequality in the second term and Holder's inequality in the third term. Note that by the Burkholder-Davis-Gundy inequality and (\ref{eq:quadvarMass}) we have that,
\[ \EE[ M_t^2 ] = \mathcal{O}\left( \frac{\theta}{N} \right). \]
Hence, by using that for positive $a$ we have $a^{1/2} \leq a+1$ we can deduce that,
\begin{align*}
\frac{1}{2} \EE[ \langle 1, \overline{\eta}_t \rangle^2 ] \leq C + \frac{1}{2} \EE[t \int_0^t \langle 1, \overline{\eta}_s \rangle^2 ds ] + \mathcal{O}\left( \left(\frac{\theta}{N}\right)^{1/2} \right) +\mathcal{O}\left( \left(\frac{\theta}{N}\right)^{1/2} \right) \EE[\langle 1, \overline{\eta}_t \rangle^2].
\end{align*}
Let $\theta$ and $N$ big enough so $\theta/N < 1/16$. From the last equation we then can deduce,
\[ \frac{1}{4}\EE[ \langle 1, \overline{\eta}_t \rangle^2 ] \leq C + \frac{C}{2} t \int_0^t\EE[\langle 1, \overline{\eta}_s \rangle^2 ] ds\]
An application of Grownwall's inequality yields
\[ \EE[ \langle 1, \overline{\eta}_t \rangle^2 ] \leq C \exp(2 C t^2) \leq C \exp(2 C T^2),  \]
finishing the proof.
\end{proof}

@@

\begin{lemma} \label{PsiBoundHS}
Fix $t>0$ and let $T(t)$ be a random variable such that $\theta T(t) \sim Poisson(\theta t)$. Then:
\[ \psi^{\epsilon,x}_t(y) = \mathbb{E}\left[ p_{\epsilon^2+T(t)}(x,y)\right] \]
Moreover,
\[ \Vert \psi^{\epsilon,x}_t \Vert_\infty \leq \mathcal{O}\left( \frac{1}{(t+\epsilon^2)^{d/2}} + \frac{1}{\epsilon^2 \theta} \right) \]
\end{lemma}
\begin{proof}
The first claim of this result follows immediately from $\mathcal{L}^\theta$ being the generator of a continuous random walk, where Gaussian jumps with mean $0$ and variance $1/\theta$ arrive at rate $\theta$.

@@

For every $x,y \in \mathbb{R}^d$ and $t>0$ we have,

@@

|\psi_t^{\epsilon,x}(y) - p_{\epsilon^2+t}(x,y)| &\leq \frac{C}{\epsilon^2 \theta}\left(\psi_t^{\epsilon,x}(y) + p_{\epsilon^2+t}(x,y) + p_{3/2(\epsilon^2+t)}(x,y)+p_{3(\epsilon^2+t)}(x,y) \right)

@@

\subsection{The martingale problem for a time dependent function.}
Before proceeding we do the following observation. For any time, dependent function $\phi_t(x)$ the martingale problem for $\overline{\eta}_t$, (\ref{mgp1}), gives that
\begin{align}
\langle \overline{\eta}_t(dx), \phi_0(x)\rangle &= \langle \overline{\eta}_0(dx), \phi_t(x)\rangle +  M_t(\phi_\cdot(\cdot)) - \int_0^t \langle \partial_t \phi_{t-s}(x), \overline{\eta}_s(dx) \rangle  ds \nonumber \\ & + \int_0^t \langle \mathcal{L}^\theta \phi_{t-s}(x), \overline{\eta}_s(dx) \rangle ds+ \int_{0}^t \langle \phi_{t-s}(x)F (\rho_\epsilon*\overline{\eta}_s)(x) ) , \overline{\eta}_s(dx) \rangle ds \label{timeMGP}
\end{align}
with $M_t(\phi_\cdot(\cdot))$ a martingale with having quadratic variation:
\[ [M(\phi_\cdot(\cdot))]_t = \frac{\theta}{N}\int_0^t \langle \int_{\mathbb{R}^d} \phi_s(z)^2 q_\theta(y,dz) + \left( 1 + \frac{F(\rho_\epsilon*\overline{\eta}_s(y))}{\theta}\right) \phi_s(y)^2, \overline{\eta}_s(dy) \rangle ds \]
\section{Tightness}

\subsection{Bounds for $\{ \rho_\epsilon * \overline{\eta}_s (x)\}_{0 \leq s \leq T}$}
\begin{lemma} \label{FirstBoundLocalDensity}
Under the conditions of Theorem~\ref{TeoremOneStepConvergence} there is a constant $C>0$ (independent of $\epsilon, N, \theta, x$ and $T$) such that,
\[ \EE[ \rho_\epsilon*\overline{\eta}_t(x) ] < C \]
for all $t \in [0,T]$ and $x \in \mathbb{R}^d$.
\end{lemma}
\begin{proof}
Recall $\psi_t^{\epsilon,x}$, the solution of (\ref{AlmostHeatEquation}) with initial condition $\psi_0^{\epsilon,x}(y)=\rho_\epsilon(y-x)$. By replacing $\phi_t$ with $\psi_t^{\epsilon,x}$ in (\ref{timeMGP}) we can write,
\begin{align}
(\rho_\epsilon*\overline{\eta}_t(x)) = \langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle  + \int_0^t \langle \psi_{t-s}^{\epsilon,x}(y) F(\rho_\epsilon*\overline{\eta}_s(y)), \overline{\eta}_s(dy) \rangle ds + M_t(x) \label{MartingaleProblemMolifier}
\end{align}
where $F$ is uniformly bounded above. Hence, if we take expectation,
\begin{align}
\EE[\rho_\epsilon * \overline{\eta}_t(x)]&= \EE[\langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle] + C \EE[\int_0^t \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy) \rangle ds] \nonumber \\ & \leq  \EE[\langle p_{\epsilon^2+T(t)}(x,y),\overline{\eta}_0(dy)\rangle] + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty \EE[\sup_{0 \leq s \leq t} \langle 1, \overline{\eta}_s(dy) \rangle] ds \\ & \leq C + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty ds \label{BoundForMolifier}
\end{align}
Where in the last inequality we used Lemma~\ref{Lemma:UniformlyBoundedMass} and our first assumption on the initial condition. Furthermore, using Lemma \ref{PsiBoundHS} we can bound $\Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty$ by $C (t-s+\epsilon^2)^{-d/2}$. In dimension one the reminding term is immediately uniformly bounded. For $d=2$ we can iterate. By using again the martingale problem and the same arguments we used to get (\ref{BoundForMolifier}) we get,
\begin{equation} \label{IterationBoundPsi}
\EE[\langle \psi_{t-s}^{\epsilon,x}, \overline{\eta}_s(dy)\rangle] \leq \EE[\langle \psi_{t}^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle]  + C \int_0^s \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
\end{equation}
Hence, using (\ref{IterationBoundPsi}) in (\ref{BoundForMolifier}) gives
\begin{align*}
\EE[ \rho_\epsilon * \overline{\eta}_t(x)  ] &\leq \EE[\langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle] + \int_0^t C\langle \psi_{t}^{\epsilon,x}, \overline{\eta}_0(dy)\rangle ds + C^2 \int_0^t \int_0^s  \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du ds \\ &= (1+Ct) \EE[ \langle \psi_t^{\epsilon,x}, \overline{\eta}_0(dy) \rangle] + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du \\ &\leq C(1+t) + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
\end{align*}
which again is uniformly bounded using Lemma \ref{PsiBoundHS}. It is easy to see this iteration can be used to prove an uniform bound in any dimension.

@@

\begin{corollary}
Let $(M_t(x))_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}). Then
\[ \EE\left[ [M(x)]_t \right] \leq \frac{C \theta}{ N \epsilon^{d}} \]
where $C$ is independent of $\epsilon,\theta,N$. \label{Cor:ControlQVMQ}
\end{corollary}
\begin{proof}
Indeed, note we can explicitly write the quadratic variation of $M_t$ by,
\[ [M(x)]_t = \frac{\theta}{N} \int_0^t \langle \int_{\mathbb{R}^d} \psi_{t-s}^{\epsilon,x}(z)^2 q_\theta(y,dz) + \left(1+\frac{F(\rho_\epsilon * \overline{\eta}_s(y))}{\theta}\right)\psi_{t-s}^{\epsilon,x}(y)^2, \overline{\eta}_s(dy) \rangle  ds\]
using Lemma~\ref{PsiBoundHS} we can get the following bound,
\[ \psi_{t-s}^{\epsilon,x}(y)^2 \leq \psi_{t-s}^{\epsilon,x}(y) \frac{C}{(\epsilon^2+t-s)^{d/2}} \leq \frac{C}{\epsilon^d} \psi_{t-s}^{\epsilon,x}(y). \]
Hence, by using the last inequality the upper bound on $F(x)1_{x}$ we deduce that:
\begin{align}
[M(x)]_t &\leq \frac{C \theta}{\epsilon^d N} \int_0^t \left\{  \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy)\rangle \right\} ds 
\label{QuadVarBound} \end{align}
Taking expectations and using the bound of Lemma~\ref{FirstBoundLocalDensity} we get the result.
\end{proof}
